### 2023-06-05 resilience-safe-up.tex
up

>>>>

Without the completion-post-effective hypothesis or the pred-basis hypothesis, coverability 
becomes undecidable. For instance the coverability problem for strongly increasing well-structured nets is undecidable~\cite{FMP-ic04}.

Coverability reduce
to resilience when $\Bad = \downarrow \Bad$ and  $\Safe = \uparrow \Safe$.
Indeed $s \to^* \uparrow t$ 
reduces to $(\Safe,\Bad)$-resilience for $\Bad = \downarrow s$ and $\Safe = \uparrow t$.
